R Notebook

### 2024-05-02 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

@@

summary(regr_end1)
summary(regr_end2)
summary(regr_end3)
summary(regr_post4)

>>>>

# # Count for in-service and pre-service teachers
# # Remove duplicate cases
# distinct_df <- distinct(main, ID, gender, .keep_all = TRUE)
# 
# # Count individual cases
# case_summary <- distinct_df %>%
#   filter(ID > 200) %>% 
#   count(gender == "male")
# print(case_summary)

@@

summary(regr_preparation1)
summary(regr_end2)
summary(regr_end3)
summary(regr_post4)
